\documentclass{article}
\usepackage{parskip} % For better spacing between paragraphs

\begin{document}

\section*{Problem Statement}

\subsection*{Problem Description}

The local music scene often suffers from issues of visibility and participation. For example, it's hard for musicians-particularly those just starting out-to reach potential fans about upcoming events. Likewise, may miss out on exciting local performances due to a lack of central, accessible information about events. While some websites provide event listings or artist profiles, they don't necessarily encompass helpful features such as interactive maps, personalized recommendations, or even the tools for collaborative scheduling that would greatly benefit the local music community. Thus, artists and fans alike end up missing opportunities to connect, discover, and grow through the local music scene.

\subsection*{Proposed Solution}

Our web application, \textbf{LocalVibes}, aims to bridge the gap between artists and audiences by promoting local music events and connecting the community in a more meaningful way. LocalVibes will offer a platform for discovering and sharing events, exploring artist profiles, and supporting local talent. By providing comprehensive features, the app seeks to connect artists and fans and propel the local music scene to new heights.



\textbf{Key features include:}

\begin{itemize}
    \item \textbf{Event Listings by Genre}: Users can filter events by genre, making it easy to find shows that match their musical preferences.
    \item \textbf{Artist Profiles \& Media}: Musicians can create detailed profiles that include bios, embedded music, and information on upcoming performances.
    \item \textbf{Interactive Event Map}: Users can explore shows by location, discovering events at venues, house parties, or other unique spaces.
    \item \textbf{Personalized Event Recommendations}: The app suggests events based on user preferences, past attendance, and listening habits.
    \item \textbf{Collaborative Gig Scheduling for Artists}: A scheduling tool that allows musicians to coordinate joint performances or plan multi-artist events.
    \item \textbf{Fan-Generated Content}: Fans can upload photos and reviews of shows, fostering a more engaged and active community.
    \item \textbf{Event Sharing \& RSVP}: Facilitates social media sharing of events and allows users to RSVP, helping artists and venues plan more effectively.
    \item \textbf{Music Networking Hub}: Connects artists, fans, and promoters, fostering collaboration and a strong music community.
    \item \textbf{Music Scene Analytics}: Provides insights on event attendance and music trends to help artists optimize their gig planning.
    \item \textbf{New Artist Showcase}: Features emerging talent in the local scene, giving new artists a platform to reach a wider audience.
\end{itemize}


By offering a platform that integrates event discovery, artist support, and community engagement, LocalVibes aims to strengthen the local music ecosystem and bring people closer to the music they love.

\subsection*{Why This Matters}

Supporting the local music scene is vital for fostering cultural diversity, creativity, and a sense of community. Many talented artists struggle to gain visibility, while music lovers often miss out on discovering great live music. By promoting local events and making it easier for artists and fans to connect, LocalVibes helps cultivate a thriving music culture. The platform empowers artists to reach new audiences, supports the financial sustainability of local talent, and encourages people to participate in cultural events, thereby enriching the community and enhancing the local music experience.

\end{document}